\documentclass{beamer}
\usepackage[utf8]{inputenc}
 
 
%% Title
\title{AWS Lambda}
\subtitle{What It Is and Why It's Terrible}
\author{Robert D. French}
\institute{Old Man Yells at Cloud, Inc.}
\date{2020}
 
 
\begin{document}
\frame{\titlepage}

\begin{frame}
	\frametitle{The Allegations}
	The \emph{Serverless} ethos is a response to alleged shortcomings of traditional
	web apps:
	\begin{itemize}
		\pause \item Patching servers is hard.
		\pause \item Scaling servers is hard.
		\pause \item Money spent on idle VMs is wasted.
	\end{itemize}
	\pause
	We'll accept these claims for the moment, because they motivate Lambda's design.
\end{frame}

\begin{frame}
	\frametitle{Some Skepticism}
	\begin{itemize}
		\item If your team is bad at these, will a new platform will be easier?
		\pause \item If you are willing to learn Serverless, why not UNIX?
	\end{itemize}
\end{frame}
 
\section{Firecracker}
\frame{\sectionpage}

\begin{frame}
	\frametitle{Cold Start}
	``A single Firecracker microVM can be launched in 125 ms\ldots You'd be
	hard-pressed to find something faster.''
	- \href{https://www.techrepublic.com/article/aws-firecracker-10-things-every-tech-pro-should-know/}{Brandon Vigliarolo / Tech Republic}
\end{frame}

\begin{frame}
	\frametitle{Firecracker}
	You can't imagine how disappointed I was to find out that they \emph{didn't} fix
	User Namespaces.
\end{frame}
 
\section{Criticism}
\frame{\sectionpage}

\begin{frame}
	Include rebuttle from @myoung34 here
\end{frame}

\end{document}
